% Default font size, values from 8-12pt are recommended
\documentclass[9pt]{developercv} 
\begin{document}

\begin{minipage}[t]{0.36\textwidth}
	% TITLE AND CONTACT INFORMATION
	% 36% of the page width for name
	\vspace{-\baselineskip}
	% Required for vertically aligning minipages
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Mansour}}}}} % First name
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Mahboubi}}}}} % Last name
	\vspace{6pt}

	% Career or current job title
	{\Large\textbf Backend engineer}
\end{minipage}
\begin{minipage}[t]{0.35\textwidth}
	% 27.5% of the page width for the first row of iconss
	% Required for vertically aligning minipages
	\vspace{-\baselineskip}

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	\icon{MapMarker}{12}{Paris / France}\\
	% \icon{Phone}{12} {\href{tel:33749455070}{+33 749 45 50 70}}\\
	\icon{At}{12}{\href{mailto:mansourmahboubi@outlook.com}{mansourmahboubi@outlook.com}}\\
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/mansourmahboubi/}{mansourmahboubi}}\\
\end{minipage}
\begin{minipage}[t]{0.27\textwidth}
	% 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip}
	% Required for vertically aligning minipages

	\small
	\icon{Globe}{12}{\href{https://mansourmahboubi.github.io/}{mansourmahboubi.github.io}}\\
	\normalsize
	\icon{Github}{12}{\href{https://github.com/mansourmahboubi}{mansourmahboubi}}\\
	% \icon{Twitter}{12}{\href{https://twitter.com/@mans0urplus}{@mans0urplus}}\\
	% \icon{BirthdayCake}{12}{1995/05/14}
\end{minipage}
\vspace{0.5cm}
%	INTRODUCTION
\cvsect{Who Am I?}

\begin{minipage}[t]{1\textwidth}
	% 40% of the page width for the introduction text
	\vspace{-\baselineskip}
	% Required for vertically aligning minipages
	I am a software developer with over five years of experience, starting my career fueled by a passion for GNU/Linux, and later developing a deep appreciation for typing systems in duck-typed languages. \\
	I have worked on data-oriented applications using Python, Django, React, and other technologies. \\
	My experience spans the education and finance industries, and I am highly enthusiastic about contributing to startups.
\end{minipage}

%	SKILS

\cvsect{Skils}
% TODO: manual enter
\\\\
\begin{minipage}[t]{0.49\textwidth}
	\Large
	% 49% of the page width for the first row of icons
	% Required for vertically aligning minipages
	\vspace{-\baselineskip}

	% The first parameter is the FontAwesome icon name, the second is the text
	\faCircle \; {Git}\\
	\faCircle \; {Python}\\
	\faCircle \; {Django}\\
	\faCircle \; {Github-actions}\\
	\faCircle \; {Docker}\\
	\faCircle \; {Azure}\\
	% \faCircle \; {REST}\\
	% \faCircle \; {OAuth}\\
	% GCP
	% Cloud native
\end{minipage}
\begin{minipage}[t]{0.50\textwidth}
	\Large
	% 50% of the page width for the second row of icons
	\vspace{-\baselineskip}
	% Required for vertically aligning minipages

	% \faCircle \; {AWS}\\
	% \faCircle \; {GraphQL}\\
	\faCircle \; {AWS}\\
	\faCircle \; {LPIC-2}\\
	\faCircle \; {Javascript}\\
	\faCircle \; {Typescript}\\
	\faCircle \; {React}\\
	\faCircle \; {Serverless}\\
	% \faCircle \; {Redux}\\
	% \faCircle \; {React-native}\\
	% \faCircle \; {Next.js}\\
	% \faCircle \; {MUI}\\
	% \faCircle \; {Storybook}\\
\end{minipage}

%	EXPERIENCE
\cvsect{Experience}
\begin{entrylist}
	\entry
	{7/2023 -- Present}
	{Payment Tech Lead - Full-time}
	{
		\href{https://www.linkedin.com/company/welcome-place/}{Welcome Place - Paris, France / On-site}}
	{
		Welcome Place is a community-driven neobank providing simple, inclusive financial solutions for newcomers in Europe. \\
		-- Main contact with compnay's payment providers to deliver SEPA, VISA integrations.\\
		-- Used EDA to make sure all the b2b updates are stored properly.\\
		-- Contributed in the impleentation of the client support using generative AI (llm).\\
		-- Leading the technical strategy and architecture of the platform. \\
		-- Used terraform to deploy the infrasctrucre in the AZURE Cloud. \\
		-- Mentoring a team of developers to follow clean code and best practices. \\
		-- Ensuring scalability and reliability. \\
		\texttt{python}\slashsep
		\texttt{typescript}\slashsep
		\texttt{aws}\slashsep
		\texttt{llm}\slashsep
		\texttt{terraform}\slashsep
		\texttt{kubernetes}\slashsep
		\texttt{azure}\slashsep
		\texttt{serverless}\slashsep
		\texttt{eda}\slashsep
		\texttt{terraform}\slashsep
	}
		\entry
	{12/2022 -- 6/2023}
	{Backend Engineer - Full-time}
	{
		\href{https://www.linkedin.com/company/lobium/}{Lobium - United Kingdom / Remote}}
	{
		Lobium was an early-stage startup focused on developing a platform for exploring and analyzing European parliament amendments. \\
		-- Spearheaded development of a data pipeline using Airflow to scrape and extract data from European websites, storing in Neo4j. \\
		-- Enhanced Neo4j queries, reducing latency from 10s to 2s. \\
		-- Guided developers in REST API development following OpenAPI guidelines. \\
		-- Deployed Neo4j using Terraform and AWS Auto Scaling Groups for scalability. \\
		-- Managed API specifications communication with front-end team. \\
		\texttt{python}\slashsep
		\texttt{neo4j}\slashsep
		\texttt{airflow}\slashsep
		\texttt{aws}\slashsep
		\texttt{terraform}
	}
	\entry
	{8/2020 -- 10/22}
	{Co-founder \& CTO - Full-time}
	{\href{https://remotion.live/}{Remotion.live - Paris / France }}
	{Remotion pivoted to build an Integrated Assessments system to manage online exams in one place.
		\href{https://remotion.live/} {Remotion I-Assess} \\\\
		% -- Choosing company techstack and setting developing rules. \\
		-- Developing a pythonic Identity provider for client integration using oauth2. \\
		-- Designing the micro-servises based on business needs such as processing the videos, managing the exams, creating the quiz. \\
		-- Leading the front-end devlopers to develop the product based on the services. \\
		-- Deploying services using GCP \\
		-- Leading developers and interns. \\
		-- Developing a django based application using GCP Vision API to process the people emotions \\
		-- Developing \href{https://analyse.remotion.live/} {Remotion Analyse} to process live emotions in the clients browser. \\
		\texttt{typescript}\slashsep
		\texttt{react}\slashsep
		\texttt{tensorflow-js}\slashsep
		\texttt{cra}\slashsep
		\texttt{gcp-vision-api}\slashsep
		\texttt{python}\slashsep
		\texttt{django}\slashsep
		\texttt{flask}\slashsep
		\texttt{tensorflow}\slashsep
		\texttt{typescript}\slashsep
		\texttt{react}\slashsep
		\texttt{next-js}\slashsep
		\texttt{REST-API}\slashsep
		\texttt{gcp}\slashsep
	}
	% \entry
	\entry
	{4/2020 -- 11/2020}
	{Software engineer - Full-time}
	{
		\href{https://www.linkedin.com/company/avid-technology-development/}{AVID Arvand - Tehran / Iran}}
	{
		AvidArvand is an international software development company with over 30 years of experience creating content-based platforms and services. \\
		Developing a new microservice for the Knito suite, which was responsible for socialization in the application.\\
		-- Developing a new app based on OCR which helped
		the company increase the speed of manufacturing. \\
		% -- Benchmarking the technologies to find the best fit for the service. \\
		-- Participating in designing the service architecture and database schema. \\
		-- Participating in developing the service using prisma-js and Graphql \\
		-- Integrating the application authentication with keycloak \\
		-- Leading new developers. \\
		
		\texttt{python}\slashsep
		\texttt{django}\slashsep
		\texttt{typescript}\slashsep
		\texttt{react}\slashsep
		\texttt{kubernetes}\slashsep
		\texttt{docker}\slashsep
		\texttt{nodejs}\slashsep
		\texttt{postgreSQL}\slashsep
		\texttt{nest-js}\slashsep
		\texttt{GraphQL}\slashsep
		\texttt{prismajs}\slashsep
		\texttt{redis}\slashsep
		}
		\entry
		{6/2019 -- 4/2020}
		{Fullstack Python developer - Full-time}
		{}
		{
			I was the maintainer of KNITO studio, a part of Knito Digital Book Store.
			\href{https://knito.com/}{knito.com} \\
		-- Customising Keycloak's (SSO) front-end with react-js and new UI. \\
		-- Adding multi-tenancy support to the STUDIO \\
		-- Adding interactive elements to the EPUB \\
		-- Integrating the application with SSO and other microservices. \\
		-- Developing new features such as Referencing inside the epub, advanced features for HTML Table, etc. \\
		-- Debugging the old code and maintaining CI/CD \\
		\texttt{kubernetes}\slashsep
		\texttt{docker}\slashsep
		\texttt{django}\slashsep
		\texttt{postgreSQL}\slashsep
		\texttt{redis}\slashsep
		\texttt{drone}\slashsep
		\texttt{Javascript}\slashsep
		\texttt{react}\slashsep
		\texttt{celery}\slashsep
		\texttt{aws}\slashsep
	}
	% \entry
	% {6/2018 -- 4/2019}
	% {Software developer - Full-time}
	% {\href{https://crypovira.com/en}{Cryptovira - Tehran / Iran}}
	% {
	% 	Cryptovira the way you manage your portfolio by automating your trading strategy. \\
	% 	-- Design an scheduler system based on celery. \\
	% 	-- Developing a service to trigger the required actions based on dynamic strategies. \\
	% 	-- Developing custom trading algorithms. \\
	% 	-- Developing auto trader system with binance public api. \\

	% 	\texttt{python}\slashsep
	% 	\texttt{django}\slashsep
	% 	\texttt{celery}\slashsep
	% 	\texttt{docker}\slashsep
	% 	\texttt{pandas}\slashsep
	% 	\texttt{binance}\slashsep
	% }
\end{entrylist}


\cvsect{Freelance Experience}
\begin{entrylist}
	\entry
	{2019}
	{React-native developer}
	{{\href{https://www.sakhtafzarmag.com/}{Sakhtafzarmag.com}}}
	{
		Sakhtafzarmag is an online magazine. \\
		-- Developing an RSS reader apllication \\
		\texttt{React-native}\slashsep
		\texttt{Wordpress-REST-Api}\slashsep
	}
\end{entrylist}
\begin{entrylist}
	\entry
	{2020}
	{Fullstack developer}
	{{\href{https://www.nilee.app/}{Nilee.app}}}
	{
		GEO location based mobile application \\
		\texttt{React-native}\slashsep
		\texttt{Django}\slashsep
		\texttt{Redis}\slashsep
		\texttt{Firebase}\\
	}
\end{entrylist}

\cvsect{Education}
\begin{entrylist}
	\entry
	{2014 -- 2019}
	{Bachelor's Degree}
	{University of Tehran}
	{
		Information Technology engineering \\
		Thesis: Intro to DevOps, and comparing container-based virtualization and serverless \\
		Activities and societies: \\
		-- Assistant for database course 2019 \\
		-- Member of IT Association 2015 - 2017 \\
	}
	% \entry
	% {2009 -- 2013}
	% {Graduate Diploma}
	% {Shahed highscool of Rasht (Komeil)}
	% {Mathematics and Physic \\}
\end{entrylist}



\cvsect{BSC projects}

\begin{entrylist}
	\entry
	{12/2015}
	{Advanced Programing}
	{University of Tehran}
	{system for managing students in CPP}
\end{entrylist}
\begin{entrylist}
	\entry
	{12/2016}
	{Artificial intelligence}
	{University of Tehran}
	{A rival for tic-tac-toe in JAVA}
\end{entrylist}


\newpage

\cvsect{Volunteer Experience}
\begin{entrylist}
	\entrytwocol
	{IT consultant}
	{Whiteheart charity}
	{Ghalbe sefid is an Iranian NGO Which is helping labour children. \\
		-- Design a bot for Institute campaigns \\
		-- Consultant Institute for IT infrustructure}

	\entrytwocol
	{Member of Guilan PUG - gilpug.gitlab.io}
	{
		{{\href{https://www.instagram.com/p/B89LgJhlW_N/}{Guilan Python user group}}}
	}
	{
		-- Organizing public sessions \\
		-- Presenting Intro to Django in the second session
	}
	\entrytwocol
	{Member of organization team}
	{{{\href{https://freelanday.ir/}{Freeland}}}}
	{Freeland is a public conference which is trying to bring freelancers together.}
\end{entrylist}

% \hfill

\cvsect{Licenses and Certifications}

\begin{entrylist}
	\entry
	{2/2022}
	{Preparing for Google Cloud Certification: Cloud Architect}
	{Coursera}
	{{\href{https://www.coursera.org/account/accomplishments/professional-cert/267M9V4HDDRW}{Credential ID 267M9V4HDDRW}}}
	% \entry
	% {3/2020}
	% {Machine Learning with Python}
	% {Coursera}
	% {{\href{https://www.coursera.org/account/accomplishments/records/8KNW27XHXTVF?utm_medium=Certificate}{Credential ID be53a654782772626b3d4e038d5e53f4j}}}
	\entry
	{3/2019}
	{LPIC-2}
	{ARJANG institute}
	{{\href{''}{Certificate ID e5khkv6brsyr74vwpw3j}}}
	% \entry
	% {2019}
	% {Data Analysis with Python}
	% {Cognitiveclass.ai}
	% {{\href{https://cognitiveclass.ai/courses/data-analy.sis-python}{Find more}}}
	% \entry
	% {12/2017}
	% {Introduction to writing business plan}
	% {University of Tehran}
	% {A course which I was also a member of operation team.}.
	% \entry
	% {10/2015}
	% {Introduction to web programming}
	% {University of Tehran}
	% {A course which I was also a member of operation team.}
	% \entry
	% {10/2015}
	% {Introduction to trading}
	% {Tehran Institute Of Technology}
	% {Amateur trading using technical analysis}
	% \entry
	% {12/2017}
	% {Python Programming}
	% {ARJANG institute}
	% {{\href{http://gotoclass.ir/Certificates/se5gmateouym2rorblxw/}{Certificate ID se5gmateouym2rorblxw}}}

	% \entry
	% {1/2018}
	% {LPIC-1}
	% {ARJANG institute}
	% {{\href{http://gotoclass.ir/Certificates/992xzjyjss6ih59y4nvt/}{Certificate ID 992xzjyjss6ih59y4nvt}}}
\end{entrylist}

%	ADDITIONAL INFORMATION

\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}

	\textbf{English} - Working proficiency\\
	\textbf{French} - B1 level\\
	\textbf{Persian} - Native\\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Hobbies}

	I love running, biking and building simpler life using new technologies\\
	I trade in stock markets in my free time.
\end{minipage}
\end{document}
