\vspace{0.2cm}

\cvsect{Experience}

\begin{entrylist}
    \entry
    {7/2023 -- Present}
    {Payment Tech Lead - Full-time}
    {
        \href{https://www.linkedin.com/company/welcome-place/}{Welcome Place - Paris, France / On-site}}
    {
        Welcome Place is a community-driven neobank providing simple, inclusive financial solutions for newcomers in Europe. \\

        -- Architected and implemented cloud infrastructure using Terraform and Azure ensuring 99.9\% uptime \\
        -- Designed and deployed event-driven microservices architecture using EDA patterns, improving system reliability and enabling real-time payment processing \\
        -- Used clean architecture to design the microservices and implemented DDD principles \\
        -- Established CI/CD pipelines using GitHub Actions and Azure DevOps, reducing deployment time from hours to minutes \\
        -- Implemented comprehensive monitoring and logging using Azure Monitor and Application Insights, reducing incident response time by 50\% \\
        -- Mentored development team in cloud-native practices and infrastructure as code \\
        -- Orchestrated integration of payment systems (SEPA, VISA) using secure cloud architecture, ensuring PCI compliance and zero security incidents \\
        \texttt{azure}\slashsep
        \texttt{aws}\slashsep
        \texttt{terraform}\slashsep
        \texttt{kubernetes}\slashsep
        \texttt{serverless}\slashsep
        \texttt{github-actions}\slashsep
        \texttt{azure-devops}\slashsep
        \texttt{eda}\slashsep
        \texttt{python}\slashsep
        \texttt{typescript}\slashsep
        \texttt{llm}\slashsep
    }
    \entry
    {12/2022 -- 6/2023}
    {Backend Engineer - Full-time}
    {
        \href{https://www.linkedin.com/company/lobium/}{Lobium - United Kingdom / Remote}}
    {
        Lobium was an early-stage startup focused on developing a platform for exploring and analyzing European parliament amendments. \\
        -- Designed and implemented data pipeline architecture using Airflow and Python, processing 10k+ documents from European parliament sources \\
        -- Developed scalable cloud infrastructure using AWS and Terraform, enabling real-time data processing and analysis \\
        -- Optimized graph database queries and data models in Neo4j, reducing query latency from 10s to 2s and improving data accessibility \\
        -- Implemented RESTful API using OpenAPI standards, enabling efficient data access and integration for frontend applications \\
        -- Established automated data quality checks and monitoring using Python and AWS services, ensuring data integrity \\
        -- Deployed containerized microservices using Docker and AWS ECS, improving system reliability and deployment efficiency \\
        \texttt{python}\slashsep
        \texttt{airflow}\slashsep
        \texttt{neo4j}\slashsep
        \texttt{aws}\slashsep
        \texttt{terraform}\slashsep
        \texttt{docker}\slashsep
        \texttt{ecs}\slashsep
        \texttt{rest-api}\slashsep
        \texttt{openapi}\slashsep
        \texttt{github-actions}\slashsep
    }
    \entry
    {8/2020 -- 10/2022}
    {Co-founder \& CTO - Full-time}
    {\href{https://remotion.live/}{Remotion.live - Paris / France }}
    {Remotion pivoted to build an Integrated Assessments system to manage online exams in one place.
        \href{https://remotion.live/} {Remotion I-Assess} \\\\
        % -- Choosing company techstack and setting developing rules. \\
        -- Developing a pythonic Identity provider for client integration using oauth2. \\
        -- Designing the micro-servises based on business needs such as processing the videos, managing the exams, creating the quiz. \\
        -- Leading the front-end devlopers to develop the product based on the services. \\
        -- Deploying services using GCP \\
        -- Leading developers and interns. \\
        -- Developing a django based application using GCP Vision API to process the people emotions \\
        -- Developing \href{https://analyse.remotion.live/} {Remotion Analyse} to process live emotions in the clients browser. \\
        \texttt{typescript}\slashsep
        \texttt{react}\slashsep
        \texttt{tensorflow-js}\slashsep
        \texttt{cra}\slashsep
        \texttt{gcp-vision-api}\slashsep
        \texttt{python}\slashsep
        \texttt{django}\slashsep
        \texttt{flask}\slashsep
        \texttt{tensorflow}\slashsep
        \texttt{typescript}\slashsep
        \texttt{react}\slashsep
        \texttt{next-js}\slashsep
        \texttt{REST-API}\slashsep
        \texttt{gcp}\slashsep
    }
    % \entry
    \entry
    {4/2020 -- 11/2020}
    {Software engineer - Full-time}
    {
        \href{https://www.linkedin.com/company/avid-technology-development/}{AVID Arvand - Tehran / Iran}}
    {
        AvidArvand is an international software development company with over 30 years of experience creating content-based platforms and services. \\
        Developing a new microservice for the Knito suite, which was responsible for socialization in the application.\\
        -- Developing a new app based on OCR which helped
        the company increase the speed of manufacturing. \\
        % -- Benchmarking the technologies to find the best fit for the service. \\
        -- Participating in designing the service architecture and database schema. \\
        -- Participating in developing the service using prisma-js and Graphql \\
        -- Integrating the application authentication with keycloak \\
        -- Leading new developers. \\

        \texttt{python}\slashsep
        \texttt{django}\slashsep
        \texttt{typescript}\slashsep
        \texttt{react}\slashsep
        \texttt{kubernetes}\slashsep
        \texttt{docker}\slashsep
        \texttt{nodejs}\slashsep
        \texttt{postgreSQL}\slashsep
        \texttt{nest-js}\slashsep
        \texttt{GraphQL}\slashsep
        \texttt{prismajs}\slashsep
        \texttt{redis}\slashsep
    }
    \entry
    {6/2019 -- 4/2020}
    {Fullstack Python developer - Full-time}
    {}
    {
        I was the maintainer of KNITO studio, a part of Knito Digital Book Store.
        \href{https://knito.com/}{knito.com} \\
        -- Customising Keycloak's (SSO) front-end with react-js and new UI. \\
        -- Adding multi-tenancy support to the STUDIO \\
        -- Adding interactive elements to the EPUB \\
        -- Integrating the application with SSO and other microservices. \\
        -- Developing new features such as Referencing inside the epub, advanced features for HTML Table, etc. \\
        -- Debugging the old code and maintaining CI/CD \\
        \texttt{kubernetes}\slashsep
        \texttt{docker}\slashsep
        \texttt{django}\slashsep
        \texttt{postgreSQL}\slashsep
        \texttt{redis}\slashsep
        \texttt{drone}\slashsep
        \texttt{Javascript}\slashsep
        \texttt{react}\slashsep
        \texttt{celery}\slashsep
        \texttt{aws}\slashsep
    }
    % \entry
    % {6/2018 -- 4/2019}
    % {Software developer - Full-time}
    % {\href{https://crypovira.com/en}{Cryptovira - Tehran / Iran}}
    % {
    % 	Cryptovira the way you manage your portfolio by automating your trading strategy. \\
    % 	-- Design an scheduler system based on celery. \\
    % 	-- Developing a service to trigger the required actions based on dynamic strategies. \\
    % 	-- Developing custom trading algorithms. \\
    % 	-- Developing auto trader system with binance public api. \\

    % 	\texttt{python}\slashsep
    % 	\texttt{django}\slashsep
    % 	\texttt{celery}\slashsep
    % 	\texttt{docker}\slashsep
    % 	\texttt{pandas}\slashsep
    % 	\texttt{binance}\slashsep
    % }
    \entry
    {2019}
    {React-native developer - Freelance}
    {{\href{https://www.sakhtafzarmag.com/}{Sakhtafzarmag.com}}}
    {
        Sakhtafzarmag is an online magazine. \\
        -- Developing an RSS reader apllication \\
        \texttt{React-native}\slashsep
        \texttt{Wordpress-REST-Api}\slashsep
    }
    \entry
    {2019}
    {Fullstack developer}
    {{\href{https://www.nilee.app/}{Nilee.app}}}
    {
        GEO location based mobile application \\
        \texttt{React-native}\slashsep
        \texttt{Django}\slashsep
        \texttt{Redis}\slashsep
        \texttt{Firebase}\\
    }
\end{entrylist}


% \cvsect{Volunteer Experience}
% \begin{entrylist}
%     \entrytwocol
%     {IT consultant}
%     {Whiteheart charity}
%     {Ghalbe sefid is an Iranian NGO Which is helping labour children. \\
%         -- Design a bot for Institute campaigns \\
%         -- Consultant Institute for IT infrustructure}

%     \entrytwocol
%     {Member of Guilan PUG - gilpug.gitlab.io}
%     {
%         {{\href{https://www.instagram.com/p/B89LgJhlW_N/}{Guilan Python user group}}}
%     }
%     {
%         -- Organizing public sessions \\
%         -- Presenting Intro to Django in the second session
%     }
%     \entrytwocol
%     {Member of organization team}
%     {{{\href{https://freelanday.ir/}{Freeland}}}}
%     {Freeland is a public conference which is trying to bring freelancers together.}
% \end{entrylist}